Write title here

### 2022-01-11 manuscript/paper.tex
Add Bui 2014 bouncing cube example
Stack of cylinders fix. Add new Rigid fluid coupling benchmarks. In progress
Implement new contact force law and validate examples

\section{Mathematical details}
\label{sec:sph}

\section{Results and discussion}
\label{sec:results}

\subsection{Benchmark 1}
\label{sec:benchmark-1}

@@

>>>>

\section{Fluid mechanics}
\label{sec:fluid-mechanics}

\section{Rigid body dynamics}
\label{sec:rbd-dynamics}

\subsection{A rigid body on a boundary}

Consider a square rigid body on a surface, the density of the body is 800
kg$m^{-3}$, the simulation is in 2 dimensions. The side of the body is
$0.5$m. The stiffness in the normal direction is $10^5$N$m^{-1}$.

\textbf{The analysis corresponding to the current section is done in file
  code $rigidbodyonasurface.py$}

\section{Rigid body contact model}
\label{sec:rbd-contact-model}

In the SPH literature there are a few ways to model the contact
between rigid bodies. Few ways to note are

\begin{itemize}
\item \citet{albano2016modelling} models using pure elastic impingement force
% Development of the Resolved Fluid-Solid SPH Coupling using Rigid Body Dynamics
\item \citet{choidevelopment} models using DEM
\item \citet{zhan2020sph} uses hybrid contact model
\item \citet{} uses hybrid contact model
\end{itemize}
A  SPH  framework  for  dynamic interaction  between  soil  and  rigid  body  system  with  hybrid contact   metho

\section{Rigid fluid coupling}
\label{sec:rf-coupling}

\section{Results and discussion}
\label{sec:results}
\citet{wu2014two} has experimental solution to cube sinking and cube floating
in a tank.

\begin{enumerate}
\item Stack of cylinders (\citet{canelas2016sph}, \citet{wang2019numerical})
\item A rigid box rotating and sinking in viscous liquid
  (\citet{sun2015numerical})
\item Water entry of 2-D cylinder (\citet{sun2015numerical})
\item Water wedge entry (\citet{sun2015numerical})
\item Dam break flow against cubes, single cube (\citet{canelas2016sph},
  \citet{ji2019coupled})
\item Dam break flow against cubes, three cubes (\citet{canelas2016sph},
  \citet{ji2019coupled})
\item Dam break flow against cubes, six cubes (\citet{canelas2016sph},
  \citet{ji2019coupled})
\item A block of density $800.52$ floating in a steady tank
  (\citet{qiu20173d}, \citet{wang2019numerical})
\item A block of density 2000 freely falling in to a steady tank
  (\citet{qiu20173d}, \citet{wang2019numerical})
\item Cylinders in water collapsed under gravity (\citet{chen2019coupled})
\item Dam break with body transport (\citet{wang2019numerical})
\item Dam break with multiple bodies transport (\citet{wang2019numerical})
\end{enumerate}

%
\subsection{(Partially) Stack of cylinders}

Stack of cylinders (\citet{canelas2016sph}, \citet{wang2019numerical})

\begin{itemize}
\item (TODO) Automan
\item (TODO) Code implementation
\item (TODO) Write in paper
\item (TODO) Results
\end{itemize}
%
\subsection{(Partially) A rigid box rotating and sinking in viscous liquid}

A rigid box rotating and sinking in viscous liquid
  (\citet{sun2015numerical})
%
\subsection{(Partially) Water entry of 2-D cylinder}

Water entry of 2-D cylinder (\citet{sun2015numerical})
%
\subsection{(TODO) Water wedge entry}
Water wedge entry (\citet{sun2015numerical})

First preliminary creation of wedge, then by removing the boundary particles,
add the particles such that they represent better boundary for wedge

%

\subsection{(TODO) Dam break flow against cubes, single cube}
% code/dam_break_flow_against_a_single_cube.py
Dam break flow against cubes, single cube (\citet{canelas2016sph},
  \citet{ji2019coupled})
%
\subsection{(TODO) Dam break flow against cubes, three cubes}
Dam break flow against cubes, three cubes (\citet{canelas2016sph},
  \citet{ji2019coupled})
%
\subsection{(TODO) Dam break flow against cubes, six cubes}
Dam break flow against cubes, six cubes (\citet{canelas2016sph},
  \citet{ji2019coupled})
%
\subsection{(TODO) A block of density $800.52$ floating in a steady tank}
A block of density $800.52$ floating in a steady tank
  (\citet{qiu20173d}, \citet{wang2019numerical})
%
\subsection{(TODO) A block of density 2000 freely falling in to a steady tank}
A block of density 2000 freely falling in to a steady tank
  (\citet{qiu20173d}, \citet{wang2019numerical})
%
\subsection{(TODO) Cylinders in water collapsed under gravity}
Cylinders in water collapsed under gravity (\citet{chen2019coupled})
%
\subsection{(TODO) Dam break with body transport}
Dam break with body transport (\citet{wang2019numerical})
%
\subsection{(TODO) Dam break with multiple bodies transport}
Dam break with multiple bodies transport (\citet{wang2019numerical})
%

@@

\section*{References}
\label{sec:references}

The adaptive fluid solid interaction is done by \citet{hu2019consistent}.
